---
title: "Image Filter Exam"
author: "Johan Lorentz"
output: html_document
---

## Aim

The algorithm reads an image, changes the RGB values pixel by pixel, and then returns a new filtered image.

The filters included are:

- greyscale
- red
- green
- blue
- cutoff filter using two colours

## Load packages and functions

```{r}
# Install these if needed:
install.packages("magick")
install.packages("devtools")

library(magick)
library(devtools)

# Load the functions from the R package folder
devtools::load_all(".")
```

## Choose image

Put your image file in the project folder and write the file name here.

```{r}
image_path <- "/Users/johan.lorentz.2/Library/CloudStorage/OneDrive-KarolinskaInstitutet/Desktop/CourseWork/GroupExam/GroupExam/Test image-1.jpg"

original_image <- image_read(image_path)
print(original_image)
```

## Apply greyscale filter

```{r}
grey_image <- filter_image(image_path, make_grey_pixel)
print(grey_image)

image_write(grey_image, "grey_image.png")
```

## Apply red filter

```{r}
red_image <- filter_image(image_path, make_red_pixel)
print(red_image)

image_write(red_image, "red_image.png")
```

## Apply green filter

```{r}
green_image <- filter_image(image_path, make_green_pixel)
print(green_image)

image_write(green_image, "green_image.png")
```

## Apply blue filter

```{r}
blue_image <- filter_image(image_path, make_blue_pixel)
print(blue_image)

image_write(blue_image, "blue_image.png")
```

## Apply cutoff filter

For this filter, the pixel is first converted to a greyscale value. If the value is below the cutoff, it becomes black. If the value is equal to or above the cutoff, it becomes pink.

```{r}
cutoff_image <- filter_image(
  image_path,
  make_cutoff_pixel,
  cutoff = 127,
  low_colour = "#000000",
  high_colour = "#FF00FF"
)

print(cutoff_image)
image_write(cutoff_image, "cutoff_image.png")
```

## Short explanation

The package separates the code into two main parts. First, there are small pixel functions, such as `make_grey_pixel()` and `make_red_pixel()`, that take one RGB pixel and return a changed RGB pixel. Second, the `change_bitmap()` function loops through the full bitmap and applies one of these pixel functions to every pixel.

This makes it possible to reuse the same bitmap-changing function with different filters.
